---
title: "linear model from Web"
author: "Trevor Ragazzo"
date: "SUMMER 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

We see the father the graph goes on the x axis higher results were seen on the y axis. We see as the ARM increases so does the SIMS.


### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

This is showing us the graph seems to be getting larger in scale by around .69

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

We fit the right equation into the line, this consist of SIMS=-4.095 + .054563 * ARM


#### Predict at target point

We predict a target value of .706544

```{r}
Pdata = data.frame(ARM=88, GRIP=94)
```

```{r}
predict(model.1, Pdata)
```
This proves our prediction to be .70

#### scatterplot with model fit
  

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
basicNN + geom_point()
basicNN + geom_point() + geom_smooth(method=lm)
```


## Model 2 SIM~GRIP

```{r}
basicNN.g <- ggplot(data,aes(y=SIMS,x=GRIP))
basicNN.g + geom_point()
basicNN.g + geom_point() + geom_smooth(method=lm)
```


### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

We see from the scatterplot that with correlation with Simms and Grip is strong


### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

We see a positive correlation between SIMMS and GRIP, but we also see that the correlation with ARMS and SIMMS is much higher.


### Inferential  (Build model.2)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

These inferential results show us that we have a standard deviation 1.295 and a Rsquared of .4053. So now we see a result of a higher Rsquared and a lower standard deviation 

#### predict model.2 at target point

```{r}
predict(model.2, Pdata)
```


#### now add the model fit to our plot for model.2
  
```{r}
basicNN.g <- ggplot(data,aes(y=SIMS,x=GRIP))
basicNN.g + geom_point()
basicNN.g + geom_point() + geom_smooth(method=lm)
```

## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
  
  The correlation we see from the numerical results are having ARM+GRIP is much higher than we would get with anything by itself.
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

lm(formula = SIMS= -5.433871 + .037311 * ARM .024470 * GRIP, data = data )


#### predict model.3 at target point
  
```{r}
predict(model.3, Pdata)
```

The prediction that we see is the combination ARM + GRIP is the lowest at -2.13, and the higher plots seem to be 2.43 

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

